### 2011-09-25 doc/theses/vitasek/chapter-3-mip.tex
Thesis: in progress.

TODO define \textit{name(AM)}

@@

@@

@@

\subsubsection{\heu{FIDAX}}

@@

\subsection{Improvement Heuristics}

@@

>>>>

\begin{define}[$name()$]
Given an attribute mapping $m = M_{x}^{y}$, $name(m)$ shall be defined as the string $x\-y$.
\end{define}

@@

For each AM $m$ there will be one binary variable $x_{name(m)}$. Objective function coefficients in vector $\mathbf{c}$ will be weights of respective mappings. For each pair of AMs $m_1, m_2$ that cannot share the same ID set (because of conflicting type or image) there shall be a row in matrix $A$ representing the inequality $x_{name(m_1)} + x_{name(m_2)} \leqslant 1$. $\mathbf{b}$ will be a vector of ones with corresponding length.

\[
\mathbf{x} =
\begin{bmatrix}
x_{y-a} \\
x_{y-b} \\
x_{y-c} \\
x_{z-a} \\
\end{bmatrix},
\mathbf{c} = 
\begin{bmatrix}
weight(M_{y}^{a}) \\
weight(M_{y}^{b}) \\
weight(M_{y}^{c}) \\
weight(M_{z}^{a}) \\
\end{bmatrix} =
\begin{bmatrix}
0.2 \\
0.2 \\
0.6 \\
0.4 \\
\end{bmatrix},
\mathbf{b} =
\begin{bmatrix}
1 \\
1 \\
1 \\
1 \\
\end{bmatrix},
A =
\begin{pmatrix}
0 & 1 & 1 & 0 \\
1 & 0 & 1 & 0 \\
1 & 1 & 0 & 0 \\
1 & 0 & 0 & 1 \\
\end{pmatrix}
\]

The problem is, recall, to solve the following.

\begin{eqnarray*}
\max_{x} z & = & \mathbf{c}^{\mathrm{T}}\mathbf{x} \\
s.t.\, A\mathbf{x} & \leqslant & \mathbf{b} \\
\end{eqnarray*}

In GLPK \textit{mathprog} language, it translates to the following formulation. % TODO cite mathprog

@@

We can use this as an input for the GLPK solver, and we get the solution: TODO GLPK output.

@@

\subsubsection{\heu{FIDAX}}
\label{section-mip-fidax}

@@

\subsection{Improvement Heuristics}
\label{section-mip-ihs}

@@

TODO mention that combination of \heu{Crossover}, \heu{Mutation} and \heu{RemoveWorst} is a sort of genetic algorithm
